---
title: "05-Exploration-of-topics-and-places"
author: "Devi Veytia"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r load libraries}
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(reticulate)
library(ggplot2)
```


# Set up data to work with

Right now I will use unique references, but ideally this should be only the included screens
```{r set up dataset}
## inputs (need to change)
sqlite.fp <- here::here("data","raw-data","sql-databases", "unique-refs_v2.sqlite")
tbl.name <- "uniquerefs"


## Get records from database
dbcon <- dbConnect(RSQLite::SQLite(), sqlite.fp, create = FALSE)
recs <- tbl(dbcon, tbl.name)


## perhaps just to on a subsample
my_text <- recs %>%
  select(analysis_id, duplicate_id, title, abstract) %>%
  slice_sample(n=100) %>%
  collect()

dim(my_text)
head(my_text)


## Clost database connection
DBI::dbDisconnect(dbcon)
```


```{r load in predicted relevance and convert to sqlite, eval=FALSE}

## Write xlsx file to a sqlite database for easy joining

predRel <- readxl::read_excel(here::here("data","raw-data","relevance-predictions","1_document_relevance_28022023.xlsx"))

# rename columns
colnames(predRel) <- c("analysis_id","relevance_mean","relevance_std","relevance_lower","relevance_upper")

predRel_db <- dbConnect(SQLite(),
                        dbname = here::here("data","raw-data","sql-databases","relevance-predictions.sqlite"),
                        create = TRUE)

dbWriteTable(predRel_db, "predRel", predRel, overwrite = TRUE)
dbDisconnect(predRel_db)
```


# Summarise relevance predictions

```{r}

## Database connection
predRel_db <- dbConnect(SQLite(), dbname = here::here("data","raw-data","sql-databases","relevance-predictions.sqlite"),create = FALSE)
predRel <- tbl(predRel_db, "predRel")


## Summaries
predRel %>%
  summarise(
    mean = sum(0.5 <= relevance_mean),
    lower = sum(0.5 <= relevance_lower),
    upper = sum(0.5 <= relevance_upper)
  )

## close database
dbDisconnect(predRel_db)

```

## Check relevance predictions

```{r compare to our manual screen results}
## Load data

# screen results
load(here::here("data","derived-data","screening","screened-records","screen_results_merged.RData")) # screen results

# metadata for all unique refs
uniqueRefs_db <- dbConnect(RSQLite::SQLite(), here::here("data","raw-data","sql-databases", "unique-refs_v2.sqlite"), create = FALSE)
uniqueRefs <- tbl(uniqueRefs_db, "uniquerefs")

# relevance predictions
predRel_db <- dbConnect(SQLite(), dbname = here::here("data","raw-data","sql-databases","relevance-predictions.sqlite"),create = FALSE)
predRel <- tbl(predRel_db, "predRel")


## Subset tables to only the columns I want
uniqueRefs <- uniqueRefs %>%
  select(analysis_id, doi)

screen_results_merged <- screen_results_merged %>%
  select(include_screen, title, year, doi, author, multiple_oro_screen, outcome_section, blue_carbon_flux_storage, sample_screen, abstract) 

predRel <- predRel


## Join dataframes together

# Join relevance predictions with metadata

# get analysis_id
screen_results_pred <- inner_join(screen_results_merged, uniqueRefs, by = "doi", copy=TRUE) 

# join to relevance predictions by analysis_id
screen_results_pred <- left_join(screen_results_pred, predRel, by = "analysis_id", copy=TRUE)



## Plot results

require(ggplot2)

ggplot(screen_results_pred %>% filter(include_screen==TRUE), aes(x= sample_screen, y=relevance_mean, fill = sample_screen)) +
  geom_violin(trim=TRUE)+
  scale_y_continuous(limits = c(0.5,1))+
  ggtitle("relevance of included articles")+
  labs(caption = "NB 2 articles with pred rel < 0.5 were truncated")+
  theme_bw()


screen_results_pred %>% 
  arrange(relevance_mean) %>% 
  mutate(id = seq(1:nrow(screen_results_pred))) %>%
  ggplot(aes(id, relevance_mean))+ 
  geom_ribbon(aes(ymin = relevance_lower, ymax = relevance_upper), alpha = 0.5, fill="pink")+
  geom_point(size=1, alpha = 0.3)+
  geom_hline(yintercept = 0.5, col="darkgrey")+
  facet_wrap(vars(include_screen))+
  ggtitle("relevance predictions for screened abstracts")+
  theme_bw()

```


# Extracting occurrence of key terms from articles

## Process text

```{r source functions}
functionsToSource <- c("clean_string.R", "screen.R","tokenization.R","utils.R")
for(i in 1:length(functionsToSource)){
  source(here::here("R", functionsToSource[i]))
}

```


```{r get corresponding title and abstract info for predicted relevance greater than 0.5}
require(dbplyr)

## Get tables from databases
dedup_db <- dbConnect(RSQLite::SQLite(),
                      here::here("data","raw-data","sql-databases", "unique-refs_v2.sqlite"), 
                                 create=FALSE)
src_dbi(dedup_db)
dedups <- tbl(dedup_db, "uniquerefs")

predRel_db <- dbConnect(SQLite(), dbname = here::here("data","raw-data","sql-databases","relevance-predictions.sqlite"),create = FALSE)
predRel <- tbl(predRel_db, "predRel")



## Filter and join

# subset to the records I want to join (pred rel => 0.5)
relRefs <- predRel %>%
  select(analysis_id, relevance_mean) %>%
  filter(0.5 <= relevance_mean) 

# use join to retreive metadata for those records
my_text <- left_join(relRefs, dedups %>% select(analysis_id,title, abstract), by = "analysis_id", copy=TRUE)
my_text <- my_text %>%
  collect()


## Disconnect databases
dbDisconnect(dedup_db)
dbDisconnect(predRel_db)


## Write to file
#save(my_text, file = here::here("data","raw-data","relevance-predictions","include_text.RData"))

```


I assembled a list of keywords grouped by different descriptive factors we would like to extract information about. We then scanned the article title, abstract and keywords and counted the occurrences of matches to these terms (boolean response of "yes" for at least one match/article).

```{r clean text}

## Load spreadsheet of keywords to extract and clean the text
nlp_search_terms <- read.csv(here::here("data","derived-data","coding","keyword-matches","keyword-search-tokens.csv"))
nlp_search_terms <- na.omit(nlp_search_terms,nlp_search_terms) # remove empty spaces
nlp_search_terms$Term <- textstem::lemmatize_strings(nlp_search_terms$Term) # lemmitize
nlp_search_terms$Term <- clean_string(nlp_search_terms$Term) # remove punctuation and extra spaces
nlp_search_terms <- nlp_search_terms[!duplicated(nlp_search_terms$Term),] # remove any resulting duplicates
nlp_search_terms$Term <- uk2us::convert_uk2us(nlp_search_terms$Term) # transform everything to American spelling

# separate out into single terms and expressions
single_words <- nlp_search_terms$Term[which(nlp_search_terms[,4] == "single")]
expressions <- nlp_search_terms$Term[which(nlp_search_terms[,4] == "expression")]
# name them by their corresponding group
names(single_words) <- nlp_search_terms$`Group name`[which(nlp_search_terms[,4] == "single")]
names(expressions) <- nlp_search_terms$`Group name`[which(nlp_search_terms[,4] == "expression")]



## Process the text to screen

# group title, abstract together
nlptxt <- my_text %>%
  mutate(text = paste(title, abstract))%>%
  select(duplicate_id, text)

# Lemmitization and clean string to remove extra spaces, numbers and punctuation
nlptxt$text <- clean_string(nlptxt$text)
nlptxt$text <- textstem::lemmatize_strings(nlptxt$text)

```


## Screen for keywords

These keyword occurrences are extracted using the code ross_keyword_extract.R. 


## Visualizing keyword search results

identify numbers of papers relevant to each topic. The tokens to search for are stored in /data/derived-data/coding/keyword-matches/keyword-search-tokens.csv. 

```{r lookup table of groups for different keywords}
nlp_search_terms <- read.csv(here::here("data","derived-data","coding","keyword-matches","keyword-search-tokens.csv"))


## Process terms so that they match the column names in the sqlite database
colnames(nlp_search_terms) <- c("Group","Group name", "Term","Term type")
nlp_search_terms <- na.omit(nlp_search_terms,nlp_search_terms) # remove empty spaces
nlp_search_terms$Term <- textstem::lemmatize_strings(nlp_search_terms$Term) # lemmitize
nlp_search_terms$Term <- clean_string(nlp_search_terms$Term) # remove punctuation and extra spaces
nlp_search_terms <- nlp_search_terms[!duplicated(nlp_search_terms$Term),] # remove any resulting duplicates
nlp_search_terms$Term <- uk2us::convert_uk2us(nlp_search_terms$Term) # transform everything to American spelling
nlp_search_terms$Term <- gsub(" ","_", nlp_search_terms$Term)


## Change names of some groupings

# change groupings of mitigation keywords
nlp_search_terms$`Group name`[
  which(nlp_search_terms$`Group name` %in% c("removal","CO2 removal from seawater",
                                   "OIF","blue carbon","bioenergy"))
] <- "carbon removal or storage"


## Names for each of the papers
topicNames <- c(
  "R&D vs implementation of mitigation OROs",
  "Biodiv & NCP outcomes",
  "Restoration practices",
  "Coastal community adaptation portfolio"
)

```

```{r connect to database with the keyword matches}
## Connect to database
keywordCon <- RSQLite::dbConnect(RSQLite::SQLite(), 
                                 dbname = here::here("data","derived-data","coding","keyword-matches","keyword-matches.sqlite"))
src_dbi(keywordCon)

keywordMatches <- tbl(keywordCon, "keywordMatches")

```

Now visualize these results 
```{r create an object to store all the plots}
ggp_list <- list()
```


For paper 1, I just want a barchart, and then the total number with any occurrence
```{r paper 1}
## Identify which paper
PaperNumber=1
Paper = paste0("Paper", PaperNumber)
tempTitle <- paste0(letters[PaperNumber],". Paper ", PaperNumber, ": ",topicNames[PaperNumber], collapse="")



## Calculate tabulation summaries

paper_df <- keywordMatches %>%
  # select only columns pertaining to paper 1
  select(analysis_id, nlp_search_terms$Term[which(nlp_search_terms$Group == Paper)]) %>%
  #head() %>%
  collect() %>%
  # format into long form with columns for id, Term and value (y/n)
  reshape2::melt(id.vars = "analysis_id", variable.name = "Term") %>%
  filter(value > 0) %>%
  # merge with grouping information for each term
  merge(nlp_search_terms, by="Term", all = FALSE)
  
nrow(paper_df)  

# by keyword group (Group name) tabulate how many hits there were
paper_tab <- paper_df %>%
  group_by(`Group name`) %>%
  summarise(n=n_distinct(analysis_id))

# how many articles retreived any hit
paper_total1 <- length(unique(paper_df$analysis_id))


## Display 

# plot parameters
yaxis_title <- "N matches"
ymax = sum(paper_tab$n, na.rm=T)   
yoffset = 5000


# plot
require(ggplot2)

ggp_list[[PaperNumber]] <- paper_tab %>%
  mutate(Topic = paste("Paper", PaperNumber)) %>% 
  ggplot(aes(x=Topic, y=n, fill = `Group name`)) + 
    geom_col()+
    geom_text(aes(y = ymax+yoffset, label = paste("total papers = ", paper_total1)))+
    labs(
      title = paste(strwrap(tempTitle, width = 40), collapse="\n"),
      y=yaxis_title
    )+
    ylim(0, ymax+yoffset)+
    scale_fill_brewer(type="qual", palette = PaperNumber)+
    theme(
      legend.position = "bottom",
      legend.title = element_blank(),
      axis.text.x = element_blank(),
      axis.title.x = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      panel.grid.major = element_line(colour = "grey"),
      panel.border = element_rect(colour = "black", fill="transparent")
    )
  
ggp_list[[PaperNumber]]


```


For paper 2, they want to know papers that have biodiv, ES, or both
```{r paper 2}
## Identify which paper
PaperNumber=2
Paper = paste0("Paper", PaperNumber)
tempTitle <- paste0(letters[PaperNumber],". Paper ", PaperNumber, ": ",topicNames[PaperNumber], collapse="")



## Calculate tabulation summaries

paper_df <- keywordMatches %>%
  # select only columns pertaining to paper
  select(analysis_id, nlp_search_terms$Term[which(nlp_search_terms$Group == Paper)]) %>%
  collect() %>%
  # format into long form with columns for id, Term and value (y/n)
  reshape2::melt(id.vars = "analysis_id", variable.name = "Term") %>%
  filter(value > 0) %>%
  # merge with grouping information for each term
  merge(nlp_search_terms, by="Term", all = FALSE)
  
  

# # how man articles have either or both biodiv or ncp
counts = with(paper_df, table(tapply(`Group name`, analysis_id, function(x) paste(as.character(sort(unique(x))), collapse=' & '))))
counts = as.data.frame(t(counts))
colnames(counts) <- c("Topic", "Group name","n")
counts$Topic <- paste("Paper", PaperNumber)


# # by keyword group (Group name) tabulate how many hits there were
# paper_tab <- paper_df %>%
#   group_by(`Group name`) %>%
#   summarise(n=n_distinct(analysis_id))


# how many articles retreived any hit
paper_total <- length(unique(paper_df$analysis_id))



# plot parameters
yaxis_title <- "N matches"
ymax = sum(paper_tab$n, na.rm=T)   
yoffset = 5000

# plot
require(ggplot2)

ggp_list[[PaperNumber]] <- counts %>%
  #mutate(Topic = paste("Paper", PaperNumber)) %>% 
  ggplot(aes(x=Topic, y=n, fill = `Group name`)) + 
    geom_col()+
    geom_text(aes(y = n, label=paste(n),group = `Group name`), position = position_stack(vjust=0.5))+
    #geom_text(aes(x=paste("Paper", PaperNumber), y = ymax+yoffset, label = paste("total papers = ", paper_total)))+
    labs(
      title = paste(strwrap(tempTitle, width = 40), collapse="\n"),
      y=yaxis_title
    )+
    #ylim(0, ymax+yoffset)+
    scale_fill_brewer(type="qual", palette = PaperNumber)+
    theme(
      legend.position = "bottom",
      legend.title = element_blank(),
      axis.text.x = element_blank(),
      axis.title.x = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      panel.grid.major = element_line(colour = "grey"),
      panel.border = element_rect(colour = "black", fill="transparent")
    )
  
ggp_list[[PaperNumber]]

```


For paper 3, do the same as for paper 2
```{r paper 3}
## Identify which paper
PaperNumber=3
Paper = paste0("Paper", PaperNumber)
tempTitle <- paste0(letters[PaperNumber],". Paper ", PaperNumber, ": ",topicNames[PaperNumber], collapse="")



## Calculate tabulation summaries

paper_df <- keywordMatches %>%
  # select only columns pertaining to paper
  select(analysis_id, nlp_search_terms$Term[which(nlp_search_terms$Group == Paper)]) %>%
  collect() %>%
  # format into long form with columns for id, Term and value (y/n)
  reshape2::melt(id.vars = "analysis_id", variable.name = "Term") %>%
  filter(value > 0) %>%
  # merge with grouping information for each term
  merge(nlp_search_terms, by="Term", all = FALSE)
  
  

# # how man articles have either or both biodiv or ncp
counts = with(paper_df, table(tapply(`Group name`, analysis_id, function(x) paste(as.character(sort(unique(x))), collapse=' & '))))
counts = as.data.frame(t(counts))
colnames(counts) <- c("Topic", "Group name","n")
counts$Topic <- paste("Paper", PaperNumber)


# # by keyword group (Group name) tabulate how many hits there were
# paper_tab <- paper_df %>%
#   group_by(`Group name`) %>%
#   summarise(n=n_distinct(analysis_id))


# how many articles retreived any hit
paper_total <- length(unique(paper_df$analysis_id))



# plot parameters
yaxis_title <- "N matches"
ymax = sum(paper_tab$n, na.rm=T)   
yoffset = 5000

# plot
require(ggplot2)

ggp_list[[PaperNumber]] <- counts %>%
  #mutate(Topic = paste("Paper", PaperNumber)) %>% 
  ggplot(aes(x=Topic, y=n, fill = `Group name`)) + 
    geom_col()+
    geom_text(aes(y = n, label=paste(n),group = `Group name`), position = position_stack(vjust=0.5))+
    #geom_text(aes(x=paste("Paper", PaperNumber), y = ymax+yoffset, label = paste("total papers = ", paper_total)))+
    labs(
      title = paste(strwrap(tempTitle, width = 40), collapse="\n"),
      y=yaxis_title
    )+
    #ylim(0, ymax+yoffset)+
    scale_fill_brewer(type="qual", palette = PaperNumber)+
    theme(
      legend.position = "bottom",
      legend.title = element_blank(),
      axis.text.x = element_blank(),
      axis.title.x = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      panel.grid.major = element_line(colour = "grey"),
      panel.border = element_rect(colour = "black", fill="transparent")
    )
  
ggp_list[[PaperNumber]]

```


```{r paper 4}

## Identify which paper
PaperNumber=4
Paper = paste0("Paper", PaperNumber)
tempTitle1 <- paste0(letters[PaperNumber],". Paper ", PaperNumber, ": ",topicNames[PaperNumber], collapse="")
tempTitle2 <- paste0(letters[PaperNumber+1],". Paper ", PaperNumber, ": ",topicNames[PaperNumber], collapse="")



## Calculate tabulation summaries

paper_df <- keywordMatches %>%
  # select only columns pertaining to paper 
  select(analysis_id, nlp_search_terms$Term[which(nlp_search_terms$Group == Paper)]) %>%
  #head() %>%
  collect() %>%
  # format into long form with columns for id, Term and value (y/n)
  reshape2::melt(id.vars = "analysis_id", variable.name = "Term") %>%
  filter(value > 0) %>%
  # merge with grouping information for each term
  merge(nlp_search_terms, by="Term", all = FALSE)

# how many articles retreived any hit
paper_total4 <- length(unique(paper_df$analysis_id))


nrow(paper_df)


## Format to visualize as a heatmap
library(reshape2)
paper_tab <- paper_df[!duplicated(paper_df[,c("analysis_id","Group name")]),]


paper_tab_Intervention <- paper_tab[grep("Intervention",paper_tab$`Group name`),c("analysis_id","Group name")]
colnames(paper_tab_Intervention)[2] <- c("Intervention")
paper_tab_Intervention$Intervention <- gsub("Intervention: ","",paper_tab_Intervention$Intervention)

paper_tab_Population <- paper_tab[grep("Population",paper_tab$`Group name`),c("analysis_id","Group name")]
colnames(paper_tab_Population)[2] <- c("Population")
paper_tab_Population$Population <- gsub("Population: ","",paper_tab_Population$Population)

paper_tab_Threat <- paper_tab[grep("threat",paper_tab$`Group name`),c("analysis_id","Term")]
colnames(paper_tab_Threat)[2] <- c("Threat")


paperMerge <- merge(paper_tab_Intervention, paper_tab_Population, by="analysis_id")
paperMerge <- merge(paperMerge, paper_tab_Threat, by="analysis_id")


## Display
library(stringr)

# Visualize Population by intervention
ggp_list[[PaperNumber]] <- paperMerge %>%
  group_by(Intervention, Population) %>%
  summarise(n=n()) %>%
  ggplot(aes(Population, Intervention, fill=n)) +
  geom_tile() +
  scale_fill_viridis_c()+
  scale_y_discrete(labels = function(x) str_wrap(x, width=10))+
  geom_text(aes(label = n), col="red")+
  labs(title = paste(strwrap(tempTitle1, width = 40), collapse="\n"),
       caption = paste("total articles = ", paper_total4))+
  theme(
      legend.position = "na",
      legend.title = element_blank(),
      #axis.text.x = element_blank(),
      #axis.title.x = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      panel.grid.major = element_line(colour = "grey"),
      panel.border = element_rect(colour = "black", fill="transparent")
    )


# Visualise threat by intervention
ggp_list[[PaperNumber+1]] <- paperMerge %>%
  group_by(Intervention, Threat) %>%
  summarise(n=n()) %>%
  ggplot(aes(Threat, Intervention, fill=n)) +
  geom_tile() +
  scale_fill_viridis_c()+
  scale_y_discrete(labels = function(x) str_wrap(x, width=10))+
  geom_text(aes(label = n), col="red")+
  labs(title = paste(strwrap(tempTitle2, width = 40), collapse="\n"),
       caption = paste("total articles = ", paper_total4))+
  theme(
      legend.position = "na",
      legend.title = element_blank(),
      axis.text.x = element_text(angle=45,hjust=1),
      #axis.title.x = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      panel.grid.major = element_line(colour = "grey"),
      panel.border = element_rect(colour = "black", fill="transparent")
    )
ggp_list[[PaperNumber+1]]
```

```{r create all plots together}

pdf(file = here::here("data","derived-data","coding","keyword-matches","keyword-matches-plots.pdf"),
    width = 10, height=15)
egg::ggarrange(
  plots = ggp_list,
  nrow=3,
  newpage=FALSE
)
dev.off()

```


```{r close databset connection}
## Close connection
RSQLite::dbDisconnect(keywordCon)

```



```{r clean environment}
rm(list=ls())
```


# Geoparsing text


Repeat the set up chunk from the beginning of the doc to load files
```{r set up dataset}
## inputs (need to change)
sqlite.fp <- here::here("data","raw-data","sql-databases", "unique-refs_v2.sqlite")
tbl.name <- "uniquerefs"


## Get records from database
dbcon <- dbConnect(RSQLite::SQLite(), sqlite.fp, create = FALSE)
recs <- tbl(dbcon, tbl.name)


## perhaps just to on a subsample
my_text <- recs %>%
  select(analysis_id, duplicate_id, title, abstract) %>%
  slice_sample(n=100) %>%
  collect()

dim(my_text)
head(my_text)

## save
write.csv(my_text,here::here("data","derived-data","coding","nlp-extracted","geocode-text.csv"))

## Clost database connection
DBI::dbDisconnect(dbcon)
```

```{r combine text for geoparsing}
my_text <- read.csv(here::here("data","derived-data","coding","nlp-extracted","geocode-text.csv"))

vec2geocode <- paste(my_text$title, my_text$abstract)
vec2geocode_duplicate_id <- my_text$duplicate_id

rm(my_text)

```



```{r clean text and remove stopwords}
#vec2geocode <- c('I went to Ottawa and then London.','Pacific northwest')


# # clean 
# vec2geocode <- clean_string(vec2geocode[1:2])
# 
# # remove stopwords
# 
# # identify stopwords
# my_stopwords <- unique(c(quanteda::stopwords(),revtools::revwords(), litsearchr::get_stopwords(), "sea", "ocean", "marine", "coast", "south", "part"))
# 
# # remove
# for(i in 1:length(vec2geocode)){
#   vec2geocode[i] <- paste(quanteda::tokens_remove(quanteda::tokens(vec2geocode[i]),
#                                                   my_stopwords),collapse = " ")
# }


```



```{r}
use_virtualenv(here::here("spaCy_env"))
#use_virtualenv(here::here("localGeocode_env"))
#use_python("C:\\Users\\deviv\\AppData\\Local\\Programs\\Python\\PYTHON~1\\python.exe")
```

Use spacy to extract components of sentences that contain locations.

Types of entity labels available:
PERSON:      People, including fictional.
NORP:        Nationalities or religious or political groups.
FAC:         Buildings, airports, highways, bridges, etc.
ORG:         Companies, agencies, institutions, etc.
GPE:         Countries, cities, states.
LOC:         Non-GPE locations, mountain ranges, bodies of water.
PRODUCT:     Objects, vehicles, foods, etc. (Not services.)
EVENT:       Named hurricanes, battles, wars, sports events, etc.
WORK_OF_ART: Titles of books, songs, etc.
LAW:         Named documents made into laws.
LANGUAGE:    Any named language.
DATE:        Absolute or relative dates or periods.
TIME:        Times smaller than a day.
PERCENT:     Percentage, including ”%“.
MONEY:       Monetary values, including unit.
QUANTITY:    Measurements, as of weight or distance.
ORDINAL:     “first”, “second”, etc.
CARDINAL:    Numerals that do not fall under another type.

attributes can be displayed using dir(doc)

First extract the entities from the text. If GPE or LOC, store seperatelyfrom dates
```{python}

import spacy
nlp = spacy.load("en_core_web_sm")


Entarr = [] ;
Datearr = [] ;


for i in range(len(r.vec2geocode)):
  doc = nlp(r.vec2geocode[i])
  
  for entity in doc.ents:
    
    if entity.label_ in ('GPE' 'LOC'):
      ents = [r.vec2geocode_duplicate_id[i], entity.label_, entity.text]
      Entarr.append(ents)
      
    if entity.label_ == 'DATE':
      ents = [r.vec2geocode_duplicate_id[i], entity.label_, entity.text]
      Datearr.append(ents)


print(Entarr[0])
print(Datearr[0])



import pickle
import os

pickle.dump(Entarr, file= open("\\".join([os.getcwd(),'data','derived-data','coding','nlp-extracted',"Entities.pickle"]), "wb"))
pickle.dump(Datearr, file= open("\\".join([os.getcwd(),'data','derived-data','coding','nlp-extracted',"Dates.pickle"]), "wb"))

del Datearr
del Entarr


```

note there will likely be duplicates in place names within a duplicate_id, so make sure to clean afterwards. Columns are: duplicate_id, entity_label, entity_text


call the output from location tagging in spacy directly to retreive metadata about the location
```{python}
from geocode.geocode import Geocode
gc = Geocode()
gc.load()

import numpy as np


Entarr = pickle.load(open("\\".join([os.getcwd(),'data','derived-data','coding','nlp-extracted',"Entities.pickle"]), "rb"))
Entarr_numpy = np.array(Entarr)

Geocodearr = [] ;

for i in range(len(Entarr)):
  location = gc.decode(Entarr_numpy[i,2])
  Geocodearr.append(location)
  

pickle.dump(Geocodearr, file= open("\\".join([os.getcwd(),'data','derived-data','coding','nlp-extracted',"Geocode-Metadata.pickle"]), "wb"))



del Geocodearr
del Entarr


```

Note also the option of gc.decode_parallel in https://github.com/mar-muel/local-geocode



Map the distribution of locations mentioned

```{python}
import pickle
import os

Entarr = pickle.load(open("\\".join([os.getcwd(),'data','derived-data','coding','nlp-extracted',"Entities.pickle"]), "rb"))
Geocodearr = pickle.load(open("\\".join([os.getcwd(),'data','derived-data','coding','nlp-extracted',"geocode-metadata.pickle"]), "rb"))

quit
```

Use r to format data frame
```{r}
require(tidyverse)

# add the duplicate id to each entry
geoarr <- list()

for(i in 1:length(py$Entarr)){
  # append each element of the list with the corresponding duplicate id -- sometimes multiple entries for each entity because returns
  # multiple matches
  tmp <- lapply(py$Geocodearr[[i]], function(x) append(x, py$Entarr[[i]]))
  # Add names to these new columns
  tmp <- lapply(tmp, function(x) {names(x)[9:11] <- c("duplicate_id","entity_label","entity_text"); x})
  geoarr[[i]] <- tmp
}

locationsDf <- flatten(geoarr)
rm(geoarr)

locationsDf <- lapply(locationsDf, function(x) as.data.frame(x))

locationsDf <- do.call(rbind.data.frame, locationsDf)


# remove any duplicated identifications within each article
# sometimes there will also be multiple values for an entity label -- in this case take the first? ****
locationsDf <- locationsDf %>%
  distinct(geoname_id, duplicate_id, entity_text, .keep_all=TRUE) 


## Format the data frame
locationsDf <- locationsDf %>%
  mutate(
    entity_label = factor(entity_label, levels=c("LOC","GPE"))
  )

## BUT geolocating only really works on GPE, not LOC types, so maybe seperate as several columns in the metadata
```


Work on coding the location types
```{r}
library(mregions)


# get records
types <- mr_place_types()

mrec <- mr_records_by_type(type = types$type[1])



# identify which records correspond to each entry
mreg_text <- locationsDf %>%
  filter(entity_label == "LOC")

mreg_code <- mregions::mr_geo_code(mreg_text$entity_text[2], fuzzy=TRUE)
mreg_code <- mreg_code[1,]


# get the area of the bounding box

library(geosphere)

xlim <- c(mreg_code$minLongitude, mreg_code$maxLongitude)
ylim <- c(mreg_code$minLatitude, mreg_code$maxLatitude)
l.out = 50

bb = rbind(cbind(xlim[1], seq(ylim[1],ylim[2],length.out = l.out)),
            cbind(seq(xlim[1],xlim[2],length.out = l.out),ylim[2]),
            cbind(xlim[2],seq(ylim[2],ylim[1],length.out = l.out)),
            cbind(seq(xlim[2],xlim[1],length.out = l.out),ylim[1]))


area <- geosphere::areaPolygon(bb)

area # in m2


# extract shp file?





save(locationsDf, file = here::here("data","derived-data","coding","nlp-extracted","geocode-metadata.RData"))
```

```{r}
library(maps)

load(here::here("data","derived-data","coding","nlp-extracted","geocode-metadata.RData"))

world_map <- map_data("world")

# # add the sizes of the different location_types
# location_size_lookup <- data.frame(
#   location_type = c('city', 'place', 'country', 'admin1', 'admin2', 'admin3', 'admin4', 'admin5', 'admin6', 'admin_other', 'continent', 'region'),
#   area  = c()
# )

ggplot()+
  geom_polygon(data = world_map, aes(x=long, y=lat, group=group), fill="grey")+

  geom_point(data=locationsDf %>% filter(entity_label == "GPE") %>% arrange(population), 
             aes(longitude, latitude, size = log(population), color = log(population)), alpha=0.3)+
  
  coord_sf()+
  scale_size_continuous()+
  scale_color_viridis_c(option = "magma")+
  theme_void()+
  guides(color = guide_legend())+
  theme(
    legend.position = c(0.1, 0.5),
      plot.background = element_rect(fill = "#f5f5f2", color = NA), 
      panel.background = element_rect(fill = "#f5f5f2", color = NA), 
      legend.background = element_rect(fill = "#f5f5f2", color = NA)
  )
  

  
```


# Junk code

Unfortunately couldn't get spacyr to work -- got stuck on spcay_install()

using: https://spacyr.quanteda.io/index.html
```{r install spaCy, eval=FALSE}
devtools::install_github("quanteda/spacyr", build_vignettes = FALSE)

library("spacyr")
spacy_install()

```


```{r use spacy to parse text and identify nouns}

library("spacyr")
spacy_initialize(model = "en_core_web_sm")

entities <- spacy_extract_entity(vec2geocode, output = "data.frame", type = "GPE")

entities

# finish spacy session
spacy_finalize()
```

