---
title: "05-Exploration-of-topics-and-places"
author: "Devi Veytia"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r load libraries}
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(reticulate)

```


# Set up data to work with

Right now I will use unique references, but ideally this should be only the included screens
```{r set up dataset}
## inputs (need to change)
sqlite.fp <- here::here("data","raw-data","sql-databases", "unique-refs_v2.sqlite")
tbl.name <- "uniquerefs"


## Get records from database
dbcon <- dbConnect(RSQLite::SQLite(), sqlite.fp, create = FALSE)
recs <- tbl(dbcon, tbl.name)


## perhaps just to on a subsample
my_text <- recs %>%
  select(duplicate_id, title, abstract) %>%
  slice_sample(n=100) %>%
  collect()

dim(my_text)


## Clost database connection
DBI::dbDisconnect(dbcon)
```


# Extracting occurrence of key terms from articles

## Process text

```{r source functions}
functionsToSource <- c("clean_string.R", "screen.R","tokenization.R","utils.R")
for(i in 1:length(functionsToSource)){
  source(here::here("R", functionsToSource[i]))
}

```

I assembled a list of keywords grouped by different descriptive factors we would like to extract information about. We then scanned the article title, abstract and keywords and counted the occurrences of matches to these terms (boolean response of "yes" for at least one match/article).

```{r clean text}

## Load spreadsheet of keywords to extract and clean the text
nlp_search_terms <- readxl::read_excel(here::here("data","derived-data","coding","keyword-search-tokens.xlsx"))
nlp_search_terms <- na.omit(nlp_search_terms,nlp_search_terms) # remove empty spaces
nlp_search_terms$Term <- textstem::lemmatize_strings(nlp_search_terms$Term) # lemmitize
nlp_search_terms$Term <- clean_string(nlp_search_terms$Term) # remove punctuation and extra spaces
nlp_search_terms <- nlp_search_terms[!duplicated(nlp_search_terms$Term),] # remove any resulting duplicates
nlp_search_terms$Term <- uk2us::convert_uk2us(nlp_search_terms$Term) # transform everything to American spelling

# separate out into single terms and expressions
single_words <- nlp_search_terms$Term[which(nlp_search_terms[,4] == "single")]
expressions <- nlp_search_terms$Term[which(nlp_search_terms[,4] == "expression")]
# name them by their corresponding group
names(single_words) <- nlp_search_terms$`Group name`[which(nlp_search_terms[,4] == "single")]
names(expressions) <- nlp_search_terms$`Group name`[which(nlp_search_terms[,4] == "expression")]



## Process the text to screen

# group title, abstract together
nlptxt <- my_text %>%
  mutate(text = paste(title, abstract))%>%
  select(duplicate_id, text)

# Lemmitization and clean string to remove extra spaces, numbers and punctuation
nlptxt$text <- clean_string(nlptxt$text)
nlptxt$text <- textstem::lemmatize_strings(nlptxt$text)

```


## Screen for keywords

```{r  screen for matches to make a document feature matrix takes a while to run}
start <- Sys.time()

screens_swd <- screen(nlptxt$text, single_words)
save(screens_swd, file=here::here("data","derived-data","coding","keyword-matches","single-word-matches.RData"))

screens_expr <- screen(nlptxt$text, expressions)
save(screens_expr, file=here::here("data","derived-data","coding","keyword-matches","expression-matches.RData"))

end <- Sys.time()

diff <- end-start
as.numeric(diff)*(300000/100)/3600 # number of hours it would take to process all records, about 2.5 hours


# # remove files
rm(screens_swd, screens_expr)

```


## Visualizing keyword search results

identify numbers of papers relevant to each topic

```{r load in screening results}
## Load and format matching results
load(here::here("data","derived-data","coding","keyword-matches","single-word-matches.RData"))
load(here::here("data","derived-data","coding","keyword-matches","expression-matches.RData"))

# order dataset according to spreadsheet
screens_all <- cbind(screens_expr, screens_swd)
screens_all <- screens_all[,match(gsub(" ","_", nlp_search_terms$Term), colnames(screens_all))]

# remove separate matrices
rm(screens_swd, screens_expr)



# some concepts require co-occurrences between two terms (i.e. AND statements)
# so make a new matrix with these values
complexTerms <- matrix(nrow=nrow(screens_all),
                       ncol = 2,
                       dimnames = list(
                         nlptxt$duplicate_id,
                         c("carbon removal or storage","coastal communities and safe space or fish")
                       ))


# for carbon AND removal

# indices of which columns contain synonyms matching relevant keywords
carb_ind <- which(nlp_search_terms$`Group name` == "carbon")
rem_ind <- which(nlp_search_terms$`Group name` == "removal")

# a y/n response for whether any of the synonymns are found
carb <- ifelse(1 <= screens_all[,carb_ind], 1,0)
rem <- ifelse(rowSums(1 <= screens_all[,rem_ind]), 1,0) 

# whether there are words matching both of the keyword groups for carbon AND removal
complexTerms[,1] <- ifelse(carb == 1 & rem == 1, 1, 0)



# for coasts and communities
coast_ind <- which(nlp_search_terms$`Group name` == "coasts")
comm_ind <- which(nlp_search_terms$`Group name` == "communities")
coast <- ifelse(rowSums(1 <= screens_all[,coast_ind]), 1,0)
comm <- ifelse(rowSums(1 <= screens_all[,comm_ind]), 1,0)
coastAndComm <- ifelse(coast == 1 & comm == 1, 1, 0)

# for safe space or fish -- i.e. other Group names that aren't coasts or communities
rest_ind <- which(nlp_search_terms$Group == "Paper4")
rest_ind <- rest_ind[which(!(rest_ind %in% c(coast_ind, comm_ind)))]
rest <- ifelse(rowSums(1 <= screens_all[,rest_ind]), 1, 0)

# for coasts and communities and safe space or fish
complexTerms[,2] <- ifelse(coastAndComm ==1 & rest == 1, 1,0)

# tablulate totals
complexTerms <- colSums(complexTerms)

## Add these new concepts in to the tabulated matrix and convert to data frame
tab_screens <- colSums(screens_all[,-c(carb_ind, rem_ind, coast_ind, comm_ind, rest_ind)])
rm(screens_all)
tab_screens <- c(tab_screens, complexTerms)
tab_screens <- as.data.frame(tab_screens)
colnames(tab_screens) <- c("n_matches")
# new vector of which paper each column belongs to
tab_screens$Topic <- c(nlp_search_terms$Group[-c(carb_ind, rem_ind, coast_ind, comm_ind, rest_ind)], "Paper1","Paper4")
tab_screens$Keyword <- rownames(tab_screens)
tab_screens$Keyword_group <- c(
  nlp_search_terms$`Group name`[-c(carb_ind, rem_ind, coast_ind, comm_ind, rest_ind)], 
  names(complexTerms)
  )
rownames(tab_screens) <- NULL
```


```{r plot the number of matches}
library(ggplot2)

# change groupings of mitigation keywords
tab_screens$Keyword_group[
  which(tab_screens$Keyword_group %in% c("CO2 removal from seawater",
                                   "OIF","blue carbon","bioenergy"))
] <- "carbon removal or storage"

topics <- unique(tab_screens$Topic)
topicNames <- c(
  "R&D vs implementation of mitigation OROs",
  "Biodiv & NCP outcomes",
  "Restoration practices",
  "Coastal community adaptation portfolio"
)


# ymax <- tab_screens %>%
#   group_by(Topic) %>%
#   summarise(n = sum(n_matches, na.rm=T))
# ymax <- ymax$n[which.max(ymax$n)]


ggp_list <- list()

for(i in 1:length(topics)){
  
  if(i %in% c(1,3)){
    yaxis_title <- "Number of matches"
  }else{
    yaxis_title <- ""
  }
  
  tempTitle <- paste0(letters[i],". Paper ", i, ": ",topicNames[i], collapse="")
  
  
  ggp_list[[i]] <- tab_screens %>%
    filter(Topic == topics[i]) %>%
    ggplot(aes(Topic, n_matches, fill = Keyword_group)) +
    geom_col()+
    labs(
      title = paste(strwrap(tempTitle, width = 40), collapse="\n"),
      y=yaxis_title
    )+
    #ylim(0, ymax)+
    scale_fill_brewer(type="qual", palette = i)+
    theme(
      legend.position = "bottom",
      legend.title = element_blank(),
      axis.text.x = element_blank(),
      axis.title.x = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      panel.grid.major = element_line(colour = "grey"),
      panel.border = element_rect(colour = "black", fill="transparent")
    )
    
}


egg::ggarrange(
  plots = ggp_list,
  nrow=2
)


```


```{r clean environment}
rm(list=ls())
```


# Geoparsing text


Repeat the set up chunk from the beginning of the doc to load files
```{r set up dataset}

```

```{r combine text for geoparsing}
geoparse_txt <- my_text %>%
  mutate(text = paste(title, abstract))%>%
  select(duplicate_id, text)
```


Test whether I can have an r object with the strings of places to decode, and then use reticulate to process this using python

```{r}
use_virtualenv(here::here("spaCy_env"))
#use_virtualenv(here::here("localGeocode_env"))
#use_python("C:\\Users\\deviv\\AppData\\Local\\Programs\\Python\\PYTHON~1\\python.exe")
```


using: https://spacyr.quanteda.io/index.html
```{r install spaCy, eval=FALSE}
devtools::install_github("quanteda/spacyr", build_vignettes = FALSE)


```

```{r}
#vec2geocode <- c('I went to Ottawa and then London.','Pacific northwest')
vec2geocode <- geoparse_txt$text

# clean 
vec2geocode <- clean_string(vec2geocode[1:2])

# remove stopwords
my_stopwords <- unique(c(quanteda::stopwords(),revtools::revwords(), litsearchr::get_stopwords(),
                       colours(), "sea", "ocean", "marine", "coast", "south", "part"))

# NOTE maybe extract nouns?? --------------


for(i in 1:length(vec2geocode)){
  vec2geocode[i] <- paste(quanteda::tokens_remove(quanteda::tokens(vec2geocode[i]),
                                                  my_stopwords),collapse = " ")
}


```

```{python test Geocode}
from geocode.geocode import Geocode
gc = Geocode()
gc.load()
gc.decode('I went to Ottawa')

```

```{python run Geocode for loop}
arr = [] ;
for input_text in r.vec2geocode:
    locations = gc.decode(input_text)
    arr.append(locations);
    

```

Note also the option of gc.decode_parallel in https://github.com/mar-muel/local-geocode

```{r}
print(py$arr[[1]])
print(vec2geocode[1])
```


Map the distribution of locations mentioned

```{r}
require(tidyverse)

# add the duplicate id to each entry
n_recs <- length(py$arr)
arr <- py$arr

for(i in 1:n_recs){
  tmp <- lapply(arr[[i]], function(x) append(x, geoparse_txt$duplicate_id[i]))
  tmp <- lapply(tmp, function(x) {names(x)[9] <- "duplicate_id"; x})
  arr[[i]] <- tmp
}

locationsDf <- flatten(arr)

locationsDf <- lapply(locationsDf, function(x) as.data.frame(x))

locationsDf <- do.call(rbind.data.frame, locationsDf)

View(locationsDf)

save(locationsDf, file = here::here("data","derived-data","coding","geoparsing","geoparsed_locations.RData"))
```

```{r}
library(maps)

world_map <- map_data("world")

# # add the sizes of the different location_types
# location_size_lookup <- data.frame(
#   location_type = c('city', 'place', 'country', 'admin1', 'admin2', 'admin3', 'admin4', 'admin5', 'admin6', 'admin_other', 'continent', 'region'),
#   area  = c()
# )

ggplot()+
  geom_polygon(data = world_map, aes(x=long, y=lat, group=group), fill="grey")+

  geom_point(data=locationsDf %>% arrange(population), 
             aes(longitude, latitude, size = log(population), color = log(population)), alpha=0.3)
  scale_size_continuous()+
  scale_color_viridis_c(option = "magma")+
  theme_void()+
  guides(color = guide_legend())+
  theme(
    legend.position = c(0.1, 0.5),
      plot.background = element_rect(fill = "#f5f5f2", color = NA), 
      panel.background = element_rect(fill = "#f5f5f2", color = NA), 
      legend.background = element_rect(fill = "#f5f5f2", color = NA)
  )
  

  
```




